% !TEX root = ../thesis_main.tex
\chapter*{Acknowledgements}

There are many people who I would like to thank for accompanying me on this journey. First off, I would like to thank Dr.\ Robert Kaindl and Dr.\ Jan Heye Buss. It was during the time I spent working with them at the Berkeley Lab that I first became aquainted with the world of ultrafast optics. Furthermore, I would like to thank Professor Junichiro Kono for providing me an opportunity to work in this exciting field of research and for his patience and guidance he showed me during the process of writing this thesis. I am also thankful to the members of my committee, Professor Hanyu Zhu and Professor R. Bruce Weisman for agreeing to serve on my committee.

I would like to extend gratitude to my fellow friends and colleagues for the support they've given me. In particular, I would like to thank Natsumi Komatsu, Dr. Weilu Gao, and Jan L{\"u}ttgens for the discussions we've had and for their efforts in preparing the samples I used in my studies. I am also grateful for the administrative support provided to me by Carol Lively, Aki Shimada, James Hayward. I also thank Dr. Gary Timothy Noe II and Fumiya Katsutani for the time and effort they have spent in mentoring me and teaching me various technical skills I used in my work. I am also grateful to Nicolas Marquez for the time he dedicated to some of the experiments we collaborated on. To the newer Kono group members Saunab Ghosh, Arash Ahmadivand, Andrey Baydin, and Fuyang Tay, it has been a pleasure getting to know you all and I wish you the best.

I would like to thank Theresa Chatman, Professor Thomas Searles and Professor Kevin Kelley for their words of encouragement. I am also grateful to my parents and my dear brother for the support they have given me over the years. Finally, I would like to acknowledge the help I've received from the Rice Counseling Center. In many ways, I know that this experience as a graduate student has left me feeling torn. I only hope that in the years to come, I will be able to look back on this moment and acknowledge that I did my very best.
